%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Blockchain Engineer} % Job title
{Korbit USA} % Organization
{Los Angeles, CA} % Location
{Jul. 2018 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item[] {At Korbit USA I am responsible for implementing backend blockchain support for the Korbit exchange, I developed a process which includes:} % Preface
\item {Cloud architecture design based on custom modules and services.}
\item {Unit and integration testing of infrastructure.}
\item {New blockchain integration and support per sprint.}
\item {Development of custom Terraform modules and services to support cloud infrastructure, forks, client updates, wallet/address management.}
\item {Development of custom API for exchange and user integration.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Blockchain Developer} % Job title
{Srax/Blockchain Identification Graph - BIG} % Organization
{Los Angeles, CA} % Location
{Nov. 2017 - Jul.2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item[] {I was responsible for the life-cycle development and implementation of the Blockchain/Ethereum infrastructure of the application.} % Preface
\item {Smart Contracts development and testing.}
\item {Deployment to Rinkeby testnet and Main net.}
\item {Web3, Geth, and Node.JS development of back end implementation and application interaction through custom API.}
\item {Developing of multi signature wallet solution dapp with React/Redux and web3.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Chief Technology Officer} % Job title
{DGF New Tech Canada Ltd.} % Organization
{Vancouver, Canada \& LA, U.S.A} % Location
{Jan. 2014 - Dec. 2017} % Date(s)
{% Description(s) of tasks/responsibilities
\begin{cvitems}
\item[] {DGF New Tech Canada specializes in remediation of industrial waste through the use of nanoparticles. Responsibilities included:} % Preface
\item {Designed and implemented scientific and engineering projects for the testing and application of different nanoparticles for remediation of contaminants.}
\item {Performed scientific validation on the efficacy of nanoparticles for the remediation of PCBs and arsenic.}
\item {Managed investment opportunities, including a multimillion dollar proposal for magnetic assisted sedimentation of mature fine tailings through the application of nanoparticles.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{High Energy Particle Physics Researcher} % Job title
{University of California, Los Angeles} % Organization
{Los Angeles, CA} % Location
{Jan. 2012 - Jan. 2014} % Date(s)
{% Description(s) of tasks/responsibilities
\begin{cvitems}
\item[] {Worked in research and development of the Cherenkov Telescope Array Prototype. Responsibilities included:} % Preface
\item {Developed custom software (C++/Qt) to analyze and interpret large data sets to aid in the calibration and alignment of telescope.}
\item {Wrote custom back end algorithms and processes to measure, analyze, and present complex data sets.}
\item {Developed data algorithms to improve calibration efficacy. Implemented solution via back end software design.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}